Patterns of floral and chromosome evolution in Onagraceae: a fossil-calibrated supermatrix analysis

### 2014-05-07 manuscript.tex
added much to results

\paragraph{Character evolution}
blah blah

\begin{table*}
   \center
   \begin{adjustbox}{max width=\textwidth}
      \setlength{\tabcolsep}{20pt}
      \begin{tabular}{lllllll}
         \toprule
	 & \multicolumn{4}{c}{Number of Petals} \\
         & 2 & 4 & 5 & 6 \\ 
	 \cmidrule{2-5}
	 Petal Color \\
         \hspace{3 mm} Pink & -0.005 & .011 & $ns$ & $ns$ \\
	 \hspace{3 mm} Yellow & -0.008 & .021 & $ns$ & $ns$ \\
	 \hspace{3 mm} White & 0.008 & 0.013 & -0.006 & -0.006 \\
	 \hspace{3 mm} Green & $ns$ & -0.011 & $ns$ & $ns$ \\
	 \hspace{3 mm} Red & $ns$ & $ns$ & $ns$ & $ns$ \\
         \bottomrule
      \end{tabular}
   \end{adjustbox}
   \caption{Test statistics for the correlation between flower color evolution and petal number evolution. 
	    $d$ values are shown
            for the pairwise comparison of states with $p< 0.01$. $ns$ indicates no significant
	    association. The overall $D$ value was 0.263 ($p=0.00$).
	    }
   \label{correlations}
\end{table*}

>>>>

\paragraph{Chromosome number evolution}
Out of the eight models of chromosome evolution tested by ChromEvol,
the four parameter $CONST\_RATE\_DEMI\_EST$ model was the best fit according to the AIC scores. 
This model has separate rate parameters for
chromosome gains ($\lambda$),
losses ($\delta$),
demi-polyploid events ($\mu$),
and polyploid events ($\rho$).
Demi-polyploid events occur when reduced and unreduced gametes unite
resulting in a $3x$ cytotype.
The base chromosome number of Onagraceae was estimated to be $x=5$,
and the ancestral number of the large genus \textit{Epilobium} was estimated to be $n=9$,
though the extant taxa are split in two large monophyletic clades of 
$n=10$ and $n=18$, respectively (Figure \ref{chromtree}).

\paragraph{Floral evolution}
The maximum likelihood estimate of petal color for the 
last common ancestor of Onagraceae was pink 
with a proportional likelihood ($PL$) of $0.61$.
White was the second most likely estimate ($PL=0.11$).
The maximum likelihood estimate of petal number for the
last common ancestor of Onagraceae was 4 ($PL=1.0$), with 15
independent transitions to 0, 2, 5, or 6 petals (Figure XXXX).
Petal color and petal number were found to significantly covary over the 
phylogeny ($D=0.263, p=0.00$). Multiple signficant correlations
($d_{ij}$) were found between individual states of each character
and are summarized in Table \ref{correlations}.

\begin{table*}
   \center
   \begin{adjustbox}{max width=\textwidth}
      \setlength{\tabcolsep}{20pt}
      \begin{tabular}{lllllll}
         \toprule
	 & \multicolumn{4}{c}{Number of Petals} \\
         & 2 & 4 & 5 & 6 \\ 
	 \cmidrule{2-5}
	 Petal Color \\
         \hspace{3 mm} Pink & -0.005 & .011 & $ns$ & $ns$ \\
	 \hspace{3 mm} Yellow & -0.008 & .021 & $ns$ & $ns$ \\
	 \hspace{3 mm} White & 0.008 & 0.013 & -0.006 & -0.006 \\
	 \hspace{3 mm} Green & $ns$ & -0.011 & $ns$ & $ns$ \\
	 \hspace{3 mm} Red & $ns$ & $ns$ & $ns$ & $ns$ \\
         \bottomrule
      \end{tabular}
   \end{adjustbox}
   \caption{Test statistics for the correlation between petal color evolution and petal number evolution. 
	    $d_{ij}$ values are shown
            for the pairwise comparison of states with $p< 0.01$. $ns$ indicates no significant
	    association. The overall $D$ value was 0.263 ($p=0.00$).
	    }
   \label{correlations}
\end{table*}
